% CV in LaTeX
\documentclass[12pt]{article} % article with 12pt font
%% PACKAGES %%
\usepackage[english]{babel} % multilingual support
\usepackage[utf8]{inputenc} % encoding
\usepackage{blindtext} % to insert blind text
% Set the default font
\usepackage{tgpagella}
% set the page layout
\usepackage{geometry}
\usepackage{hyperref}
\geometry{
  a4paper,
  left=20mm,
  %right=
  %bottom=
  top=15mm}
  % empty the headers, footers, pagenumbers…
\pagestyle{empty}
% Custom sectioning with secsty
\usepackage{sectsty}

\sectionfont{%                        
    \large % make sections smaller
    \fontfamily{qag}\selectfont % change font family
    \sectionrule{0pt}{0pt}{-5pt}{1pt} % insert a thin rule
}
%% MACROS %%


% size of the boxes used to align text
\newlength{\spacebox}
\settowidth{\spacebox}{123456789}
% vertical space separator between entries
\newcommand{\sepspace}{\vspace*{1em}}
% name
\newcommand{\name}[1]{
\Huge % font size
\fontfamily{phv}\selectfont % font family
% print name centered and bold
\begin{center} \textbf{#1} \end{center}\par
% back to normal size and font
\normalsize\normalfont}
  % personal information
\newcommand{\info}[2]{
  % set specific indentation for personal information
    \noindent\hangindent=2em\hangafter=0
  % create a box to align two pieces of text
    \parbox{\spacebox}{%
    \textsl{#1}} % slanted entry name
    #2 \par} % entry value
    % skill
\newcommand{\skill}[2]{
  % set specific indentation for personal information
  \noindent\hangindent=2em\hangafter=0
  % create a box to align two pieces of text
  \parbox{1.8\spacebox}{% three times larger box
  \textbf{#1}} % small caps entry name
  {\small #2} \par} % entry value

% name of the work
\newcommand{\education}[4]{
\noindent  \textbf{#1}
% at the right the duration
  \newline
  \noindent \textit{#2} \par
% new paragraph with the school in italics
  \noindent #3 \par
% description with no hanging and in smaller text
\vspace*{0.5em}
  \noindent\hangindent=2em\hangafter=0 \small #4
%back to normal size
\normalsize \par}

% work experience

\newcommand{\work}[4]{
% name of the work
  \noindent  \textbf{#1}
% at the right the duration
  \newline
  \noindent \textit{#2} \par
% new paragraph with the school in italics
  \noindent #3 \par
% description with no hanging and in smaller text
\vspace*{0.5em}
  \noindent\hangindent=2em\hangafter=0 \small #4 
%back to normal size
\normalsize \par}

\newcommand{\personalstatement}[1]{
  \vspace*{0.5em}
  \noindent\hangindent=2em\hangafter=0 \small #1 
\normalsize \par}

\newcommand{\interests}[1]{
  \vspace*{0.5em}
  \noindent\hangindent=2em\hangafter=0 \small #1 
}

\begin{document}

% name and motto
\name{Peter Gillingham}
\vspace*{-10pt}

% personal information
\sepspace
\info{Email}{\texttt{petergillingham80@gmail.com}}
\info{Phone}{07383 014163}
\info{LinkedIn}{\texttt{\url{www.linkedin.com/in/peter-gillingham}}}
\info{GitHub}{\texttt{\url{https://github.com/PeterG184}}}

% personal statement
\section*{Personal Statement}
\personalstatement{I am a software developer, with a broad skillset including full stack web development, data science and analysis with Python and MATLAB, and embedded systems engineering with C and C++. I graduated from the University of York, awarded an Upper Second Class Honours for an Integrated Masters in Electronic Engineering with Music Systems Technology. In my career so far I have successfully integrated myself into fast paced environments, working with many technologies across multiple areas of software engineering, including front and back end web development, implementation of AI solutions and in research on networking in embedded devices.}
% \personalstatement{As a software engineer, I possess a comprehensive skill set, encompassing expertise in full-stack web development, AI and computer vision tooling, embedded systems design, and proficient database management. I graduated with Upper Second Class Honours from the University of York, completing an Integrated Masters in Electronic Engineering with Music Technology Systems. Throughout my career, I have thrived in the dynamic environment of a fast-paced startup, excelling in rapid development cycles and meeting tight deadlines.}

% work experience
\section*{Work Experience}
\work{Research Software Engineer}{April 2024--Present}{University of York}{I work across multiple projects. I and the lead developer in the implementation of a solar panel data tracking dashboard, designing the database, developing the APIs for access and creating the frontend for visualisation, as well as using machine learning techniques for predicting energy generation and usage. I also develop software for experiments involving embedded networking devices, working to test jamming attacks and developing countermeasures to them.}
\work{Software Engineer}{August 2023--February 2024}{Premium Lithium}{I have worked across many disciplines in this role, developing full stack web applications, leading multiple projects in operations management and internal statistic tracking, and implementing AI applications for energy arbitrage and solar panel detection. It was a fast paced start up requiring me to manage my time effectively, meet ever changing requirements and deadlines, and work as part of an agile team.}
\work{Production Operator}{October 2021--August 2023}{DJ Assembly}{I worked in all areas of production and manufacturing of electronic goods, including circuit assembly, equipment building, and inspection, testing and validation. I also gained experience in managing outgoing and internal stock and logistics.}

% education
\section*{Education}

\education{Integrated Master's in Electronic Engineering with Music Systems Technology}{September 2019--June 2023}{University of York}{This course has taught me and improved my knowledge in many areas, including electronics, software development, hardware implementation, embedded system design, networking, digital signal processing and data analysis. \\}

\education{A Levels - Computer Science, Mathematics and History}{September 2017--June 2019}{Moulsham High School}{}

\education{9 GCSEs including English and Mathematics}{September 2012--June 2017}{Moulsham High School}{}

% technical skills
\section*{Technical skills}

\skill{Languages}{Python (Pandas, Numpy), JavaScript/TypeScript (Node.js, React, SvelteKit), C, C\#, Java, MATLAB and SQL}
\skill{Technologies}{Git, Linux, PostgreSQL, .NET, AWS, Google Cloud Compute, Vercel}
\skill{Software}{Object Oriented Programming, Agile Methodology, Algorithm Design, Database Design and Management}
\skill{Engineering}{Circuit Design and Analysis, Hardware and Software Integration, Embedded System Design and Development}

\section*{Achievements}
\begin{itemize}
  \item Led a project to develop an AI driven energy arbitrage algorithm for use in homes to manage the purchasing and storing of generated energy.
  \item Investigated vulnerabilities in Thread Network devices, developing a console and GUI utility for controlling embedded devices, and implementing jamming attacks and countermeasures in a testbed thread network.
  \item Set up data collection of a solar farm, including energy and weather data in a Dockerised MySQL database, alongside a web based (React) frontend and Python API for visualisation and data retrieval, and trained energy usage and generation prediction with machine learning models from the data.
  % \item Delivered multiple customer facing web applications built in SvelteKit with a PostgreSQL database.
  % \item Successfully managed and worked in a team to develop an interactive presentation system, complete with image, audio, video and text display and Python and JavaScript scripting capabilities, implemented in Java.
  % \item Created a model of the human voice and a guitar through the use of physical modelling synthesis, implemented in MATLAB.
\end{itemize}

\section*{Interests}
\interests{I have played guitar for over a decade, drums for four years, and have taken on the role of lead guitarist and audio engineer for my band, resulting in us releasing two albums and playing multiple shows in York. I am also a keen and regular climber, both in climbing gyms and outdoors, and I enjoy cycling in and around York.}

\end{document}
